\documentclass[]{article}
\usepackage[utf8]{inputenc}
\usepackage{fullpage}
%\usepackage[margin=1.1in]{geometry}
%\usepackage[subtle]{savetrees}
\usepackage[parfill]{parskip}
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{comment,todonotes,soul} 
\usepackage{bm}

\title{Mixed-Integer Geometric Programming}
\author{Miles \& Chris}
\date{}

\begin{document}
\maketitle


\section{From GP to MIGP}

gp standard form and convex form \cite{boyd07}, example - aircraft wings \cite{hoburg14a}

gp with integer variables, example - gate sizing \cite{boyd07}

generalized GP:

\begin{subequations}
\begin{gather}
\begin{align}
\min \quad \max_{S \in \mathcal{S}} \quad
\sum_{i \in S} D_i :
\end{align}
\\
\begin{align}
g_i X_i^{-1} \sum_{j \in F_i} \left( a_j + b_j X_j \right) 
& = D_i
& \forall i \in G \backslash O
\\
g_i c_i X_i^{-1} 
& = D_i 
& \forall i \in O
\\
X_i
& \geq 1
& \forall i \in G
\\
\sum_{i \in G} h_i X_i 
& \leq \bar{p}
\\
\sum_{i \in G} a_i X_i 
& \leq \bar{a}
\end{align}
\end{gather}
\end{subequations}

or GP, eliminating $D_i$:

\begin{subequations}
\begin{gather}
\begin{align}
\min \quad D :
\end{align}
\\
\begin{align}
D^{-1} \sum_{i \in S \cap O} g_i c_i X_i^{-1} + D^{-1} \sum_{i \in S \backslash O} g_i X_i^{-1} \sum_{j \in F_i} \left( a_j + b_j X_j \right)
& \leq 1
& \forall S \in \mathcal{S}
\\
X_i^{-1}
& \leq 1
& \forall i \in G
\\
\bar{p}^{-1} \sum_{i \in G} h_i X_i 
& \leq 1
\\
\bar{a}^{-1} \sum_{i \in G} a_i X_i 
& \leq 1
\end{align}
\end{gather}
\end{subequations}

now let $X_i = e^{\chi_i}, \forall i \in G$ and $D = e^{\delta}$. transform into convex form by taking $\log$ of both sides of each posynomial inequality and the objective.

\begin{subequations}
\begin{gather}
\begin{align}
\min \quad \delta :
\end{align}
\\
\begin{align}
\log \left( \sum_{i \in S \cap O} g_i c_i e^{-\chi_i} + \sum_{i \in S \backslash O} g_i e^{-\chi_i} \sum_{j \in F_i} \left( a_j + b_j e^{\chi_j} \right) \right)
& \leq \delta
& \forall S \in \mathcal{S}
\\
\chi_i
& \geq 0
& \forall i \in G
\\
\log \sum_{i \in G} h_i e^{\chi_i}
& \leq \log \bar{p}
\\
\log \sum_{i \in G} a_i e^{\chi_i}
& \leq \log \bar{a}
\end{align}
\end{gather}
\end{subequations}

where in the example problem, $O = \{6,7\}, \mathcal{S} = \left\{ \{1,4,6\}, \{1,4,7\}, \{2,4,6\}, \{2,4,7\}, \{2,5,7\}, \{3,5,6\}, \{3,7\} \right\}, F_i = \{...\}$ and $h_i = f_i e_i$, $\forall i \in G$.


can impose integer constraints on the $X_i$: a discrete number of transitors per gate: $X_i = e^{\chi_i} \in \mathbb{N}$, which implies $\chi_i \in \{ \log n \vert n \in \mathbb{N}, n > 0 \}$. note $n \geq 1$ (valid for integer problem) implies the constraint $\chi_i \geq 0$.



\section{MIDCP Formulation of MIGP}

dcp \cite{boyd06}, midcp \cite{lubin15}


the migp, in conic form, is... \hl{do we actually want to write with the expo cone?}



selection of log-integer variables not MIP-representable

assuming bounds, disjunctive constraint formulations



\section{Solution Algorithm}

solve migp like other midcp problems with pajarito, an outer approximation alg \cite{lubin15}. can migp have unbounded feasible set? would cause problems for pajarito

find (and perhaps improve during iterations) bounds on the log-integer variables (tighter bounds led to significant speed up and avoids ECOS numerical issues, for gate sizing example)



\section{Examples and Results}

small gate-sizing problem



approximate nonconvex functions piecewise, extend Woody paper \cite{hoburg14b}

Woody aircraft example



\section{Future Work}

disjunctive formulations in the MILP - what encodings are best

unbounded log-integer variables

cuts to the MILP or to the GP

mixtures of cones













\begin{thebibliography}{9}

\bibitem{boyd07}
Boyd, Stephen, et al. ``A tutorial on geometric programming.'' Optimization and engineering 8.1 (2007): 67-127.

\bibitem{hoburg14a}
Hoburg, Warren, and Pieter Abbeel. ``Geometric programming for aircraft design optimization.'' AIAA Journal 52.11 (2014): 2414-2426.

\bibitem{hoburg14b}
Hoburg, Warren, and P. Abbeel. "Fitting Geometric Programming Models to Data." Optimization and Engineering (2014).

\bibitem{lubin15}
Lubin, Miles, et al. ``Extended Formulations in Mixed-integer Convex Programming.'' arXiv preprint arXiv:1511.06710 (2015).

\bibitem{boyd06}
Grant, Michael, Stephen Boyd, and Yinyu Ye. \textit{Disciplined convex programming.} Springer US, 2006.

\end{thebibliography}

\end{document}







